The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-08 paper/ms.tex
paper update

\begin{figure}
  \includegraphics[width=0.45\textwidth]{escapefraction.png}
   \caption{Escape fraction as a function of rotational velocity. The
     continuous (dashed) lines correspond to homogeneous (central)
     models.
     \label{fig:efvsv}}
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.35]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centered emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction and the observer is
    along the $\hat{\j}$ direction (where the reader is) (THE ANGLE
    THETA IS WRONG. IT IS THE ANGLE WITH THE OBSERVER, RIGHT?). 
    \label{fig:OCspheres}} 
\end{figure}

@@

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5$R and can
have to possible centers positions $C$ along the $\hat{\i}$ direction:
$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
direction, such that the emitting sphere centered on $+C\hat{\i}$ moves
away from the observer and the sphere centered on $+C\hat{\i}$ moves
towards the observer. We consider two values for $C=(0.25,0.50)R$.

@@

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer. The most
interesting effect is that emission is that in  some models ($\tau =
10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
presents three peaks (blue-shifted,centred, red-shifted). However, we
do not find any asymmetry in the line produced by the off-center
emission. As in the homogeneous / central model the line gets broader
as the rotational velocity increases.

@@

\begin{figure*}
\includegraphics[scale=0.3]{OC_profiles.png}
\caption{\ly profiles for the off-center positions. Dashed/solide
  lines represents spheres centered at $-0,5R/+0.5R$.
   \label{fig:OC_profiles}} 
\end{figure*}

@@

>>>>

\begin{figure}
  \includegraphics[width=0.45\textwidth]{escapefraction.png}
   \caption{Escape fraction as a function of rotational velocity, for these models we took $\tau_{a}=1$. The
     continuous (dashed) lines correspond to homogeneous (central)
     models.
     \label{fig:efvsv}}
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.35]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centered emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (where the reader is) 
    and the observer is along the $\hat{\j}$ direction. 
    \label{fig:OCspheres}} 
\end{figure}

@@

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5$R and can
have to possible centers positions $C$ along the $\hat{\j}$ direction:
$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
away from the observer and the sphere centered on $+C\hat{\j}$ moves
towards the observer. We consider two values for $C=(0.25,0.50)R$.

@@

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer ($\vert \mu \vert > 0.9$ $\&$ $\vert \mu \vert < 1.0]$). The most
interesting effect is that emission in  some models ($\tau =
10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
presents three peaks (blue-shifted,centred, red-shifted). However, we
do not find any asymmetry in the line produced by the off-center
emission. As in the homogeneous / central model the line gets broader
as the rotational velocity increases.

@@

\begin{figure*}
\includegraphics[scale=0.3]{OC_profiles.png}
\caption{\ly profiles for the off-center positions. Dashed/solid
  lines represents spheres centered at $-0,5R/+0.5R$.
   \label{fig:OC_profiles}} 
\end{figure*}

\subsection{Three-Peak Profiles}

\begin{figure*}
\includegraphics[scale=0.3]{3peaks.png}
\caption{Three-Peak profiles for the off-center positions. 
   \label{fig:3p_profiles}} 
\end{figure*}

As mentioned in Sec 3.4 Off-centered emission shows signs of three peak 
profiles, to analyse this in more detail we use the same method of the spheres
explained in Sec 3.4. We select spheres at $C=\pm 0.25, 0.5, 0.75$ for all the 
models, for those who present signs of three peak profiles such as $(V_{max}=50kms^{1} 
\& \tau_{H}=10^{5}), (V_{max}=100kms^{1} \& \tau_{H}=10^{6}), (V_{max}=200kms^{1}
\& \tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ with the aim 
of get a stronger profile.

Fig. \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
a relation between optical depth, rotational velocity and $C$ must be accomplish.
In particular we found that for the outer spheres $C=\pm 0.75$ the three
peak arise for all of our models with $\tau_{\gamma}=10^{6}$. The main effect of
the rotational velocity is to give rise to the central peak. If the rotational velocity is 
high also the optical depth have to be high in order to compensate the height of the wings 
of the line with the central peak.

Finally we take into account the finite spectral resolution to see if three peaks 
profiles produced by rotation could be observed. Fig.\ref{fig:3p_res} show that even
with a low resolution a three-peak profile would be observed.

\begin{figure*}
\includegraphics[scale=0.3]{3p_res.png}
\caption{Three-Peak profiles for different resolutions. 
   \label{fig:3p_res}} 
\end{figure*}

@@

JNGC thanks the support of Universidad de los Andes given as TA
Also ISAAC 2012 summer school which provide computer time where some of this 
models where ran.
